\documentclass{article}
\usepackage[a4paper]{geometry}
\usepackage{nopageno}
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

\begin{document}

\pagestyle{plain}

\noindent\textbf{3.  Explain how this vocational arena impacts society at large, and how this vocation is strategic to Christ’s kingdom.  Provide evidence that your chosen field is under-represented by Christians and tell us how you plan to impact your field for Christ.}\\

Due to the ubiquity of its output, the field of computing has a significant impact on society.  
As of 2010, there were more than five billion mobile phone connections, all over the world\footnote{http://www.bbc.co.uk/news/10569081}.  
There are also at least two billion internet connections\footnote{http://www.engadget.com/2011/01/28/un-worldwide-internet-users-hit-two-billion-cellphone-subscript/}.
Because of the internet, people all over the world have unprecedented access to all sorts of information.
Also, due to the increasing number of sensors with which phones are equipped (e.g., GPS), people create lots of data about what they are doing.

The AMP Lab at UC Berkeley is focused on how you can use algorithms, machines, and people to make sense of big data.  
Big data is challenging to tackle because it is often heterogeneous, dirty, uncurated, inconsistent, and rapidly accumulating.
In addition, many of the questions people would like to use big data to answer are time-sensitive.
Our research agenda is shaped by applications that produce and analyze big data.
The application I am focusing on involves computational support for cancer research and treatment.
The goal of our project is to help provide personalized medicine, which is the problem of recommending a treatment based on genomic data about a person's normal and cancerous tissue.
Several large cancer datasets exist\footnote{http://cancergenome.nih.gov/, www.1000genomes.org/}; however, this data is not yet being used to help physicians reach decisions about their patients' treatment.
One hurdle currently being faced is that you need to sequence a patient's genome regularly to keep track of mutations in their tumor to see how the cancer is progressing.  
If this is to be feasible, sequencing must be affordable.
The cost of actually obtaining the genome sequence is rapidly decreasing\footnote{http://www.genome.gov/sequencingcosts/}; soon, the dominating cost will be processing the sequencing data.
To address this, my colleagues and I are working on a new sequence alignment algorithm that will provide high-accuracy alignments at low cost.

Because computing has a global reach, it is strategic to Christ's kingdom.
Almost every person on earth is a consumer of computing.
People from all over the world work in computing, and people from areas where you have few Christians such as India and China make up a significant portion of the workforce.
Thus, computing allows us to reach people who are in areas of the world that have very few Christians and may in fact be very hostile to Christians.
In addition, computing has the potential to improve people's lives, thereby bringing shalom.  
The cancer application my colleagues and I are focusing on is an example; in addition, because of the internet, people in rural areas have access to a plethora of information that can aid in their development.

Though computing is an ideal field for impacting the world for Christ, it is severely under-represented by Christians.
By one figure, about 23\% of computer science undergraduate students have a spiritual life (not necessarily Christian)%\footnote{http://books.google.com/books?id=9xip9rEcEB4C&pg=PA95&lpg=PA95&dq=percentage+christians+in+computer+science&source=bl&ots=QP47D5lT_Q&sig=4qNmi6drv4D0tEBvXbONN-tnIFA&hl=en&ei=bsaUTou8KOvWiAKbtuj-BA&sa=X&oi=book_result&ct=result&resnum=3&ved=0CDYQ6AEwAg#v=onepage&q&f=false}.
Also, CS is dominated by South and Southeast Asians, very few of whom are Christian%\footnote{http://en.wikipedia.org/wiki/Religion_in_China, http://en.wikipedia.org/wiki/Christianity_in_India}.

I believe God has called me to work in the field of computing so that He might use me to influence it for Him.
First, I try to work on problems like the cancer application that can benefit society and bring shalom.
I also take advantage of the opportunity to reach the global lost without leaving the US by sharing the gospel through word and deed with my colleagues.

\end{document}